\documentclass{ximera}
\usepackage{sagetex}
\usepackage{multicol}
%% handout
%% space
%% newpage
%% numbers
%% nooutcomes

\input{../preamble} %% we can turn off input when making a master document

\outcome{Understand and solve quadratic equations.}
\author{Darryl Chamberlain Jr.}
 
\title{Objective 3 - Solving Quadratics by Factoring}

\begin{document}
\begin{abstract}
Solving quadratic equations using the zero-factor principle.
\end{abstract}
\maketitle

\href{https://cnx.org/contents/mwjClAV_@8.1:-Sm9he1Q@17/Quadratic-Functions}{Link to section in online textbook.}

%%%%%%%%%%%%%%%%%%%%%
%%%  Objective 3  %%%
%%%%%%%%%%%%%%%%%%%%%

First, watch the video below to learn how to use factoring to solve a quadratic equation. You can \href{http://people.clas.ufl.edu/dchamberlain31/files/M4-Objective-3-Solving-Quadratics-by-Factoring.pdf}{use the notes here} to follow along with the video and record your thoughts.

\youtube{QsFAIbCApt0} 

Now practice solving quadratic equations by factoring. 

\begin{sagesilent}
x = var("x")

###########################
def maybeMakeNegative(natural):
    integer = natural*(-1)**ZZ.random_element(2)
    return integer

def generateFactors(minimumPrime, maximumPrime, numberOfFactors):
    listPrimes = [p for p in range(minimumPrime, maximumPrime+1) if is_prime(p)]
    aFactors = [listPrimes[ZZ.random_element(0, len(listPrimes))] for i in range(numberOfFactors)]
    cFactors = [listPrimes[ZZ.random_element(0, len(listPrimes))] for i in range(numberOfFactors)]
    return [aFactors, cFactors]
    
def generateSolution(minimum, maximum, numberOfFactors):
    factors = generateFactors(minimum, maximum, numberOfFactors)
    aFactors = factors[0]
    cFactors = factors[1]
    a = prod(aFactors)
    c = prod(cFactors)
    b = maybeMakeNegative(ZZ.random_element(minimum, maximum+1))
    d = maybeMakeNegative(ZZ.random_element(minimum, maximum+1))
    #This will guarantee that we always generate solutions with b < d
    if(b < d):
        return [a, b, c, d]
    else:
        return [c, d, a, b]

def generateZeros(a, b, c, d):    
    z0 = round(float(-b/a), 3)
    z1 = round(float(-d/c), 3)
    # Orders from small to large
    if z0 < z1:
        return [z0, z1]
    else:
        return [z1, z0]

def generateProblem(solution):
    a, b, c, d = solution
    return [a*c, a*d + b*c, b*d]

############ END OF DEFINITIONS ###############
numberOfFactors567 = 1
minimum = 2
maximum = 7

##### QUESTION 5 #####
solution5 = generateSolution(minimum, maximum, numberOfFactors567)
problem5 = generateProblem(solution5)
generalForm5 = problem5[0] * x**2 + problem5[1] * x + problem5[2]
zeros5 = generateZeros(solution5[0], solution5[1], solution5[2], solution5[3])

##### QUESTION 6 #####
solution6 = generateSolution(minimum, maximum, numberOfFactors567)
problem6 = generateProblem(solution6)
generalForm6 = problem6[0] * x**2 + problem6[1] * x + problem6[2]
zeros6 = generateZeros(solution6[0], solution6[1], solution6[2], solution6[3])

##### QUESTION 7 #####
solution7 = generateSolution(minimum, maximum, numberOfFactors567)
problem7 = generateProblem(solution7)
generalForm7 = problem7[0] * x**2 + problem7[1] * x + problem7[2]
zeros7 = generateZeros(solution7[0], solution7[1], solution7[2], solution7[3])

####
numberOfFactors8910 = 2

##### Question 8 #####
solution8 = generateSolution(minimum, maximum, numberOfFactors8910)
problem8 = generateProblem(solution8)
generalForm8 = problem8[0] * x**2 + problem8[1] * x + problem8[2]
zeros8 = generateZeros(solution8[0], solution8[1], solution8[2], solution8[3])

##### Question 9 #####
solution9 = generateSolution(minimum, maximum, numberOfFactors8910)
problem9 = generateProblem(solution9)
generalForm9 = problem9[0] * x**2 + problem9[1] * x + problem9[2]
zeros9 = generateZeros(solution9[0], solution9[1], solution9[2], solution9[3])

##### Question 10 #####
solution10 = generateSolution(minimum, maximum, numberOfFactors8910)
problem10 = generateProblem(solution10)
generalForm10 = problem10[0] * x**2 + problem10[1] * x + problem10[2]
zeros10 = generateZeros(solution10[0], solution10[1], solution10[2], solution10[3])
\end{sagesilent}

\begin{question}
Solve the quadratic equation below. 

	$$ \sage{generalForm5} = 0 $$

Smaller solution: $x = \answer[tolerance=0.05]{\sage{zeros5[0]}}$

Larger solution: $x = \answer[tolerance=0.05]{\sage{zeros5[1]}}$ 

\end{question}

\begin{question}
Solve the quadratic equation below. 

	$$ \sage{generalForm6} = 0 $$
	
Smaller solution: $x = \answer[tolerance=0.05]{\sage{zeros6[0]}}$

Larger solution: $x = \answer[tolerance=0.05]{\sage{zeros6[1]}}$ 

\end{question}

\begin{question}
Solve the quadratic equation below. 

	$$ \sage{generalForm7} = 0 $$
	
Smaller solution: $x = \answer[tolerance=0.05]{\sage{zeros7[0]}}$

Larger solution: $x = \answer[tolerance=0.05]{\sage{zeros7[1]}}$ 

\end{question}

%TYPE 2 (Type 3 from M2O4) - a and c are fairly composite (ac has at least 8 factors)
\begin{question}
Solve the quadratic equation below. 

	$$ \sage{generalForm8} = 0 $$
	
Smaller solution: $x = \answer[tolerance=0.05]{\sage{zeros8[0]}}$

Larger solution: $x = \answer[tolerance=0.05]{\sage{zeros8[1]}}$ 

\end{question}

\begin{question}
Solve the quadratic equation below. 

	$$ \sage{generalForm9} = 0 $$
	
Smaller solution: $x = \answer[tolerance=0.05]{\sage{zeros9[0]}}$

Larger solution: $x = \answer[tolerance=0.05]{\sage{zeros9[1]}}$ 

\end{question}

\begin{question}
Solve the quadratic equation below. 

	$$ \sage{generalForm10} = 0 $$
	
Smaller solution: $x = \answer[tolerance=0.05]{\sage{zeros10[0]}}$

Larger solution: $x = \answer[tolerance=0.05]{\sage{zeros10[1]}}$ 

\end{question}

\end{document}
